---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# Datazoom.social - R version

The datazoom.social package facilitates access to official 
Brazilian social data. The package provides functions that 
download, pre-process and edit (in research-oriented ways) 
the Continuous PNAD (Continuous National Household Sample Survey), easing comprehension and research aimed at better understanding brazillian microdata.
The Continuous PNAD is conducted through a sample of households with a rotation scheme. Thus, the same household is interviewed five times and, therefore, the same individuals are likely to be interviewed more than once. However, the identification of them is not provided. The survey is released from IBGE (Brazilian Institute of Geography and Statistics) and is produced periodically every quarter. It releases information such as the working-age population, average income, employed population, among other important indicators for socioeconomic research.


This package is in development stage - more datasets will
be released soon.

# Installation

You can install the released version of `datazoom.social` from
[CRAN](https://CRAN.R-project.org/package=datazoom.social) with:

``` {r, eval=FALSE}
install.packages("datazoom.social")
```

And the development version from GitHub with:

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("datazoompuc/datazoom.social")
```

```{r, echo=FALSE, message=FALSE}
devtools::load_all()
```

***
## Data 

<table>

<tr><td>

|||
|---|---|
| **[LOAD_PNADC](#load_pnadc)** | _Download PNAD of a specific period_ |
| **[BUILD_PNADC](#build_pnadc)** | _Build a Panel of PNAD_ |

***

# Functions

## LOAD_PNADC

```{r child = "vignettes/LOAD_PNADC.Rmd"}
```

***

## BUILD_PNADC

```{r child = "vignettes/BUILD_PNADC_PANEL.Rmd"}
```

***

# Credits

DataZoom is developed by a team at Pontifícia Universidade Católica do Rio de Janeiro (PUC-Rio), Department of Economics. Our official website is at: <https://www.econ.puc-rio.br/datazoom/>.

To cite package `datazoom.social` in publications use:

> Data Zoom (2023). Data Zoom: Simplifying Access To Brazilian Microdata.  
> https://www.econ.puc-rio.br/datazoom/english/index.html

A BibTeX entry for LaTeX users is:

``` 
@Unpublished{DataZoom2024,
	author = {Data Zoom},
	title = {Data Zoom: Simplifying Access To Brazilian Microdata},
	url = {https://www.econ.puc-rio.br/datazoom/english/index.html},
	year = {2024}}

```


