---
title: "github_document"
output: html_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# datazoom.social - R version

The datazoom.social package facilitates access to official 
Brazilian social data. The package provides functions that 
download, pre-process and edit (in research-oriented ways) 
selected datasets, easing comprehension and research aimed
at better understanding brazillian microdata.

This package is in development stage - more datasets will
be released soon.

# Installation

You can install the released version of `datazoom.social` from
[CRAN](https://CRAN.R-project.org/package=datazoom.social) with:

``` {r, eval=FALSE}
install.packages("datazoom.social")
```

And the development version from GitHub with:

```{r}
# install.packages("devtools")
devtools::install_github("datazoompuc/datazoom.social")
```

```{r, echo=FALSE, message=FALSE}
devtools::load_all()
```

# Functions

## LOAD_PNADC

```{r child = "vignettes/LOAD_PNADC.Rmd"}
```

## BUILD_PNADC

```{r child = "vignettes/BUILD_PNADC_PANEL.Rmd"}
```

# Credits

DataZoom is developed by a team at Pontifícia Universidade Católica do Rio de Janeiro (PUC-Rio), Department of Economics. Our official website is at: <https://www.econ.puc-rio.br/datazoom/>.

To cite package `datazoom.social` in publications use:

> Data Zoom (2023). Data Zoom: Simplifying Access To Brazilian Microdata.  
> https://www.econ.puc-rio.br/datazoom/english/index.html

A BibTeX entry for LaTeX users is:

``` 
@Unpublished{DataZoom2024,
	author = {Data Zoom},
	title = {Data Zoom: Simplifying Access To Brazilian Microdata},
	url = {https://www.econ.puc-rio.br/datazoom/english/index.html},
	year = {2024},
}

```


