---
title: 'BUILD_PNADC_PANEL'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MAPBIOMAS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

**Description**

The main goal of the function build_pnadc_panel is to create a Panel of PNAD where it's possible to identify each household or individual all over the interviews by a specific serial number (id) based on some variables of PNAD Continua.

The method used for the identification is based on the paper of Ribas, Rafael Perez, and Sergei Suarez Dillon Soares(2008): "Sobre o painel da Pesquisa Mensal de Emprego (PME) do IBGE". 

***

## Basic Identification

For the household identifier, it combines the variables:

* `UPA` - Primary Sampling Unit - PSU;

* `V1008` - Household ;

* `V1014` - Panel Number;

In order to create a unique number for every combination of those variables.

***

For the Individual id identifier, it combines the `household id` with:

* `UF` - Federal Unit;

* `V1023` - Type of Area;

* `V2007` - Gender;

* Date of Birth - [`V20082` (year), `V20081` (month), `V2008` (day)];

In order to create an unique number for every combination of those variables.

For identifying matched observations, the function counts the number of time that each id appears.

***

## Advanced Identification

It's only run on previously unmatched individuals for identifying new matched observations.

Advanced identification is divided in two stages:

In `Stage 1` the function combines the variables:

* `V2005` - Housing Condition;

* `V2009` - Age of Resident; 

* Date of Birth - [`V20082`, `V20081`, `V2008`].

In `Stage 2` it checks if there's any missing quarters and if there's no intersection between their appearences. In that case the function returns the id.


At last, it handles with unidentifiable observations due to missing values.


***
**Options:**

  1. **dat**: The current PNAD observations.


  2. **panel**: The type of panelling transformation you wish to apply to dat:
  
     * `none`: No panel build. Returns the original data.
     
     * `basic`: Performs basic identification steps for creating households and individual identifiers for panel construction.
     
     * `advanced`: Performs advanced identification steps for creating households and individual identifiers for panel construction.

***

**Examples:** 

```{r eval=FALSE}
# Build basic panel 
data <- read.csv("path/to/PNADC_data.csv")
 panel_data <- build_pnadc_panel(dat = data, panel = "basic")

```





