---
title: "datazoom.pnadcontinua"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{datazoom.pnadcontinua}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Panel of Individuals

The Continuous PNAD is a panel survey from Brazil's IBGE, in which each household is interviewed for five consecutive quarters.

## Usage

Start by loading the package
```{r, eval= TRUE}
library(datazoom.pnadcontinua)
``` 

### Loading data

Function ```load_pnadcontinua``` is flexible enough to process Continous PNAD stored in three forms:

* Downloading quarterly data directly from IBGE
* Reading datasets on a directory
* Reading specific .txt Continuous PNAD on the computer

To download data, be sure to set argument ```sources``` as a list of vectors, each 
one consisting on a quarter-year pairing. The function will store the raw microdata
on folder ```PNADC_microdata``` inside the directory set by ```download_directory```,
which defaults to the working directory.

```{r, eval = TRUE}
dates <- list(c(1, 2012), c(2, 2012), c(3, 2013))

loaded_data <- load_pnadcontinua(sources = dates)

# Set language = 'pt` to have the labels in Portuguese

``` 

Alternatively, set sources as a folder or a text file path. In case you set it to a folder,
the function will read all text files in it. 

```{r,  eval=FALSE}

loaded_data <- load_pnadcontinua(sources = './Desktop')

``` 

```loaded_data``` is a list of dataframes, with each element corresponding
to a different quarter and being named accordingly.


### Dictionary

The package also comes with dictionaries in English and Portuguese,
```dictionary_pnadcontinua_eng```, ```dictionary_pnadcontinua_pt.br```, with a description of all variables in the
survey, as well as of the variables assumed by them.

```{r, eval = TRUE, echo = FALSE}
head(dictionary_pnadcontinua_eng)
``` 


## Credits

Data Zoom is developed by a team at Pontifícia Universidade Católica do Rio de Janeiro (PUC-Rio), Department of Economics. Our official website is at: http://www.econ.puc-rio.br/datazoom/index.html.




